---
title: "DATA607-Assignment 7"
author: "Gavriel Steinmetz-Silber"
date: "2023-10-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Working with HTML, XML, and JSON in R

In this assignment, I picked three philosophy books. I stored information about each of the three books in three seperate files (HTML, XML, and JSON). Here, I will load the information from each of the three sources into separate R data frames.

### XML

```{r}
library(tidyverse)
library(XML)
library(httr)

temp = GET('http://raw.githubusercontent.com/gsteinmetzsilber/DATA607--Assignment7/main/books.xml')
data = xmlParse(temp, useInternal = TRUE)
headers = xpathSApply(data, "//header", xmlValue)
cells = xpathSApply(data, "//cell", xmlValue)

book1 = data.frame(t(cells))
colnames(book1) = headers
```

Here's the resulting dataframe: 

```{r}
book1
```

### HTML

```{r}
library(rvest)
book2 = read_html('https://raw.githubusercontent.com/gsteinmetzsilber/DATA607--Assignment7/main/books.html') %>% 
  html_table() %>% 
  as.data.frame()
```

And the resulting dataframe is: 

```{r}
book2
```

### JSON

```{r}
library(jsonlite)
book3 = fromJSON('https://raw.githubusercontent.com/gsteinmetzsilber/DATA607--Assignment7/main/books.json') %>% 
  as.data.frame()
```

And the dataframe:

```{r}
book3
```

## Discussion

Overall, the dataframes look identical in their structure, other than "Year" being a character (and not an int) in the dataframes stemming from the XML and JSON files. This is due in large part to how I set the tables up, at least subconsciously wanting a similar structure for all. 

While writing the files, especially XML and HTML, was arduous, loading the data was overall easy. I had the hardest time with the XML file, having to clarify the header contents and adjusting the dataframe accordingly. This may have been a function of the libraries that I chose. I had to go back into the XML file structure to write the code correctly. 

Just to illustrate that the dataframes' structures are identical (other than the "Year" type), I'll combine the dataframes into one: 

```{r}
book1 = book1 %>% 
  mutate(Year = as.numeric(Year))
book3 = book3 %>% 
  mutate(Year = as.numeric(Year))

books = bind_rows(book1, book2, book3)

books
```

